Blocking-resistant communication\\through domain fronting

### 2014-07-16 docs/meek.tex
Better phrasing.

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you are saying},
and blocking by address is based on \emph{whom you are speaking to},
A skilled censor will do both, and effective circumvention requires meeting both challenges.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.

>>>>

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by address.
Blocking by content is based on \emph{what you say},
and blocking by address is based on \emph{whom you talk to}.
A skilled censor will do both, and effective circumvention requires meeting both challenges.
A content-blocking censor inspects packets and payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is sometimes called deep packet inspection (DPI).
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
An address-blocking censor forbids all communication with certain
addresses, for example IP addresses and domain names, whatever the contents may be.
The challenge of address blocking is met by making it difficult for the censor to learn proxy addresses;
by having overwhelmingly many proxies;
or by colocating proxies with high-value services so that both must be blocked or both allowed.
